Cartesian Closed Categories as a Model for the Simply Typed Lambda Calculus

### 2017-09-20 papers/talk-9/talk-9.tex
added completeness

\iffalse
\section{Free Cartesian Closed Categories}
\label{sec:free}

\begin{theorem}
    \label{thm:compl}
    If $M|[\Gamma\type s: A|] = M|[\Gamma\type t: A|]$ for every mapping $M$ of ground types and constants and every cartesian closed category $\cat{C}$,
    then $\Gamma \type s =_{\beta\eta} t: A$.
\end{theorem}
\begin{proof}
    We give a proof sketch.

\end{proof}
\fi

>>>>

%\iffalse
\section{Free Cartesian Closed Categories}
\label{sec:free}

The soundness theorem~\ref{thm:sound} has a converse called completeness.

\begin{theorem}{(Completeness)}
    \label{thm:compl}
    If $M|[\Gamma\type s: A|] = M|[\Gamma\type t: A|]$ for every mapping $M$ of ground types and constants and every cartesian closed category $\cat{C}$,
    then $\Gamma \type s =_{\beta\eta} t: A$.
\end{theorem}
\begin{proof}
    We give a proof sketch.
    The idea is to construct a freely generated cartesian closed category $\cat{F}$ and instantiate the assumption with $\cat{F}$.
    Objects of $\cat{F}$ are types of the simply typed lambda calculus.
    The set of morphisms from $A$ to  $B$ is the quotient of the set $\{s \mid \ \type s: A \to B\}$, where two terms $s$ and $t$ are equivalent iff
    $\ \type s =_{\beta\eta} t: A \to B$ holds.
    Showing that $\cat{F}$ is a cartesian closed category concludes the proof.
\end{proof}
%\fi
